Demo arXiv template

### 2022-10-12 paper/paper.qmd
more refine

Many variables relevant to decision making cannot be directly measured, however, they are crucial for resource allocation, early prevention, and other operational purpose.
For example, fire authorities would be interested to quantify fire risk since bushfires can have a huge impact on monetary loss, health, and the local ecosystem among others.
Climatologists would be interested in monitoring the change in global conditions since variability in atmospheric and oceanic conditions has a direct impact on global weather and climate.
Usually, more than one variable is related to the concept of interest and they often need to be integrated to make decisions.
<!-- From a modelling perspective, these unobserved quantities are called latent variables and existing methods can incorporate these latent variables in the model structure.  -->
In many domains, constructing an index is a common approach to characterise these unobservable quantities.
The index approach allows researchers to compare the quantity of interest across countries and also cross time.

@@

The meaning of indices varies across disciplines and in this article, an index is defined as a tool to quantify a concept of interest that does not have a direct measure.
The concept of interest doesn't have a direct measure can because it is impractical to measure the concept of interest at the population level. 
For example, it would be nearly impossible to include all the available stocks in the market to characterise stock market behavior, indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite select a representative set of stocks to measure the overall market behavior. 
Also belonging to this category are the economic indices like the Consumer Price Index, where price changes of a basket of items are weighted to measure inflation. 
The lack of direct measure could also be due to the absence of a universal definition on the concept of interest. 
Many natural and social concepts are fundamentally multi-facets and some indices combine measures from different domains to characterise the concept of interest. 
This includes drought indices constructed from meteorological, agricultural, hydrological, and social-economic variables [give some names?]. 
Social development indices like Human Development Index [@hdi] and Global Liveability Index [@gli] measure various aspects of the quality of human capital and urban life.

Despite many measurements having the term *index* in their name, they cannot be technically classified as indices according to the definition given above. 
A major reason for these measures to lose their index memberships is that the underlying concept of interest is straightforward to measure once defined. 
Sometimes variables like precipitation of the driest month or percentage of days when maximum temperature is below a certain percentile are classified as climate indices, however, precipitation and temperature can be directly measured by rain gauge and thermometer. 
These variables are transformation on precipitation and temperature. 
They can be used to construct indices but are not indices themselves. 
Similarly, a set of remote sensing indices should not be classified as indices, but variables, since they are measures of electromagnetic wave reflectance.
This includes Normalized Difference Vegetation Index (NDVI) [@tucker_red_1979], derived from the ratio of difference over sum on two segments in the spectrum, also called band: near-infrared (NIR) and red.
So are the "indices" derived from NDVI, e.g. Vegetation Condition Index [@kogan_application_1995]. 
Notice that this does not exclude all the construction derived from remotes sensor variables to be valid indices.
For example, Vegetation Drought Response Index [@brown_vegetation_2008] is a valid index since it integrates climate, satellite, and biophysical variables to quantify vegetation stress.

TODO: clean up terminology:

  - "index" only for valid indices
  - "variable" the most generic dump????
  - "measure" for item quantified by instruments or devices in standard units

@@

  - Vegetation Condition Index  = (NDVI - NDVI_min)/ (NDVI_max - NDVI_min)
  - A measure is a variable, the variable itself is not an index. 
  - Not all multivariate "indices" are indices (i.e. those remote sensor transformations), but generally they are. It is possible that an index is constructed from a single variable (i.e. SPI), but be careful on whether it is variable or index.

>>>>

Many concepts relevant to decision making cannot be directly measured, however, they are crucial for resource allocation, early prevention, and other operational purpose.
For example, fire authorities would be interested to quantify fire risk since bushfires can have a huge impact on monetary loss, health, and the local ecosystem.
Climatologists would be interested in monitoring the change in global climate since variability in atmospheric and oceanic conditions has a direct impact on global weather and climate.
Usually this concept of interest is associated with more than one variables and these variables need to be integrated to make decisions on the subject matter.
<!-- From a modelling perspective, these unobserved quantities are called latent variables and existing methods can incorporate these latent variables in the model structure.  -->
A common approach to quantify concepts like these is to construct an index using these relevant variables. 
This allows researchers to compare the quantity of interest across entities (i.e. countries, regions) and also cross time.

@@

The meaning of indices varies across disciplines and in this article, an index is defined as a tool to quantify a concept of interest that does not have a direct measure.
The concept of interest doesn't have a direct measure can because it is impractical to measure at the population level. 
For example, it would be nearly impossible to include all the available stocks in the market to characterise stock market behavior, so indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite select a representative set of stocks to measure the overall market behavior. 
Also belonging to this category are the economic indices like the Consumer Price Index, where price changes of a basket of items are weighted to measure inflation. 
The lack of direct measure could also because the concept itself is an unobservable human construction, rather than a physical quantity that can be measured.
Many natural hazard and social concepts falls into this category. 
This includes drought indices constructed from meteorological, agricultural, hydrological, and social-economic variables, e.g. Standardised Precipitation Index (SPI) [@mckee1993relationship] and Aggregated Drought Index (ADI) [@keyantash_aggregate_2004] among others.
Social development indices like Human Development Index [@hdi] and Global Liveability Index [@gli] measure various aspects of the quality of human capital and urban life.

Despite many quantity having the term *index* in their name, they cannot be technically classified as indices according to the definition given above. 
The reason for these quantities to lose their index memberships is that they are variables can be accurately measured given the instrument precision. 
This includes quantities like precipitation of the driest month or percentage of days when maximum temperature is below 10th percentile. 
They are measures of precipitation and percentage of days under specific conditions (dries month, maximum temperature below 10th percentile).
They are variables, or indicators, that can be used to construct indices but are not indices themselves. 
Similarly, a set of remote sensing indices are not indices, since they are measures of electromagnetic wave reflectance.
This includes Normalized Difference Vegetation Index (NDVI) [@tucker_red_1979], derived from the ratio of difference over sum on two segments in the spectrum, also called band: near-infrared (NIR) and red.
So are the "indices" derived from NDVI, e.g. Vegetation Condition Index [@kogan_application_1995]. 
Notice that this does not exclude all the construction derived from remotes sensor variables to be valid indices.
For example, Vegetation Drought Response Index [@brown_vegetation_2008] is a valid index since it integrates climate, satellite, and biophysical variables to quantify vegetation stress.

@@

  - Vegetation Condition Index  = (NDVI - NDVI_min)/ (NDVI_max - NDVI_min)
  - A measure is a variable, but is not an index. 
  - Not all multivariate quantities are indices (i.e. those remote sensor measures). It is possible that an index is constructed from a single variable (i.e. SPI).
  - Indices is not a single/ set of measures

### 2022-10-12 paper/paper.tex
more refine

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, frame hidden, enhanced, boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Many variables relevant to decision making cannot be directly measured,
however, they are crucial for resource allocation, early prevention, and
other operational purpose. For example, fire authorities would be
interested to quantify fire risk since bushfires can have a huge impact
on monetary loss, health, and the local ecosystem among others.
Climatologists would be interested in monitoring the change in global
conditions since variability in atmospheric and oceanic conditions has a
direct impact on global weather and climate. Usually, more than one
variable is related to the concept of interest and they often need to be
integrated to make decisions. In many domains, constructing an index is
a common approach to characterise these unobservable quantities. The
index approach allows researchers to compare the quantity of interest
across countries and also cross time.

@@

The meaning of indices varies across disciplines and in this article, an
index is defined as a tool to quantify a concept of interest that does
not have a direct measure. The concept of interest doesn't have a direct
measure can because it is impractical to measure the concept of interest
at the population level. For example, it would be nearly impossible to
include all the available stocks in the market to characterise stock
market behavior, indices like Dow Jones Industrial Average, S\&P 500,
and Nasdaq Composite select a representative set of stocks to measure
the overall market behavior. Also belonging to this category are the
economic indices like the Consumer Price Index, where price changes of a
basket of items are weighted to measure inflation. The lack of direct
measure could also be due to the absence of a universal definition on
the concept of interest. Many natural and social concepts are
fundamentally multi-facets and some indices combine measures from
different domains to characterise the concept of interest. This includes
drought indices constructed from meteorological, agricultural,
hydrological, and social-economic variables {[}give some names?{]}.
Social development indices like Human Development Index (United Nations
Development Programme 2022) and Global Liveability Index (Economist
Intelligence Unit 2019) measure various aspects of the quality of human
capital and urban life.

Despite many measurements having the term \emph{index} in their name,
they cannot be technically classified as indices according to the
definition given above. A major reason for these measures to lose their
index memberships is that the underlying concept of interest is
straightforward to measure once defined. Sometimes variables like
precipitation of the driest month or percentage of days when maximum
temperature is below a certain percentile are classified as climate
indices, however, precipitation and temperature can be directly measured
by rain gauge and thermometer. These variables are transformation on
precipitation and temperature. They can be used to construct indices but
are not indices themselves. Similarly, a set of remote sensing indices
should not be classified as indices, but variables, since they are
measures of electromagnetic wave reflectance. This includes Normalized
Difference Vegetation Index (NDVI) (Tucker 1979), derived from the ratio
of difference over sum on two segments in the spectrum, also called
band: near-infrared (NIR) and red. So are the ``indices'' derived from
NDVI, e.g.~Vegetation Condition Index (Kogan 1995). Notice that this
does not exclude all the construction derived from remotes sensor
variables to be valid indices. For example, Vegetation Drought Response
Index (Brown et al. 2008) is a valid index since it integrates climate,
satellite, and biophysical variables to quantify vegetation stress.

TODO: clean up terminology:

\begin{itemize}
\tightlist
\item
  ``index'' only for valid indices
\item
  ``variable'' the most generic dump????
\item
  ``measure'' for item quantified by instruments or devices in standard
  units
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Vegetation Condition Index = (NDVI - NDVI\_min)/ (NDVI\_max -
  NDVI\_min)
\item
  A measure is a variable, the variable itself is not an index.
\item
  Not all multivariate ``indices'' are indices (i.e.~those remote sensor
  transformations), but generally they are. It is possible that an index
  is constructed from a single variable (i.e.~SPI), but be careful on
  whether it is variable or index.
\end{itemize}

@@

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, frame hidden, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

Many concepts relevant to decision making cannot be directly measured,
however, they are crucial for resource allocation, early prevention, and
other operational purpose. For example, fire authorities would be
interested to quantify fire risk since bushfires can have a huge impact
on monetary loss, health, and the local ecosystem. Climatologists would
be interested in monitoring the change in global climate since
variability in atmospheric and oceanic conditions has a direct impact on
global weather and climate. Usually this concept of interest is
associated with more than one variables and these variables need to be
integrated to make decisions on the subject matter. A common approach to
quantify concepts like these is to construct an index using these
relevant variables. This allows researchers to compare the quantity of
interest across entities (i.e.~countries, regions) and also cross time.

@@

The meaning of indices varies across disciplines and in this article, an
index is defined as a tool to quantify a concept of interest that does
not have a direct measure. The concept of interest doesn't have a direct
measure can because it is impractical to measure at the population
level. For example, it would be nearly impossible to include all the
available stocks in the market to characterise stock market behavior, so
indices like Dow Jones Industrial Average, S\&P 500, and Nasdaq
Composite select a representative set of stocks to measure the overall
market behavior. Also belonging to this category are the economic
indices like the Consumer Price Index, where price changes of a basket
of items are weighted to measure inflation. The lack of direct measure
could also because the concept itself is an unobservable human
construction, rather than a physical quantity that can be measured. Many
natural hazard and social concepts falls into this category. This
includes drought indices constructed from meteorological, agricultural,
hydrological, and social-economic variables, e.g.~Standardised
Precipitation Index (SPI) (McKee et al. 1993) and Aggregated Drought
Index (ADI) (Keyantash and Dracup 2004) among others. Social development
indices like Human Development Index (United Nations Development
Programme 2022) and Global Liveability Index (Economist Intelligence
Unit 2019) measure various aspects of the quality of human capital and
urban life.

Despite many quantity having the term \emph{index} in their name, they
cannot be technically classified as indices according to the definition
given above. The reason for these quantities to lose their index
memberships is that they are variables can be accurately measured given
the instrument precision. This includes quantities like precipitation of
the driest month or percentage of days when maximum temperature is below
10th percentile. They are measures of precipitation and percentage of
days under specific conditions (dries month, maximum temperature below
10th percentile). They are variables, or indicators, that can be used to
construct indices but are not indices themselves. Similarly, a set of
remote sensing indices are not indices, since they are measures of
electromagnetic wave reflectance. This includes Normalized Difference
Vegetation Index (NDVI) (Tucker 1979), derived from the ratio of
difference over sum on two segments in the spectrum, also called band:
near-infrared (NIR) and red. So are the ``indices'' derived from NDVI,
e.g.~Vegetation Condition Index (Kogan 1995). Notice that this does not
exclude all the construction derived from remotes sensor variables to be
valid indices. For example, Vegetation Drought Response Index (Brown et
al. 2008) is a valid index since it integrates climate, satellite, and
biophysical variables to quantify vegetation stress.

@@

\begin{itemize}
\tightlist
\item
  Vegetation Condition Index = (NDVI - NDVI\_min)/ (NDVI\_max -
  NDVI\_min)
\item
  A measure is a variable, but is not an index.
\item
  Not all multivariate quantities are indices (i.e.~those remote sensor
  measures). It is possible that an index is constructed from a single
  variable (i.e.~SPI).
\item
  Indices is not a single/ set of measures
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-keyantash_aggregate_2004}{}}%
Keyantash, John A., and John A. Dracup. 2004. {``An Aggregate Drought
Index: {Assessing} Drought Severity Based on Fluctuations in the
Hydrologic Cycle and Surface Water Storage.''} \emph{Water Resources
Research} 40 (9). \url{https://doi.org/10.1029/2003WR002610}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-mckee1993relationship}{}}%
McKee, Thomas B, Nolan J Doesken, John Kleist, et al. 1993. {``The
Relationship of Drought Frequency and Duration to Time Scales.''} In
\emph{Proceedings of the 8th Conference on Applied Climatology},
17:179--83. 22. Boston, MA, USA.
